### 2021-05-21 Supplementary_Material/Regression_Trees_All.Rmd
edits

rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency for all species", cex.main=1.75,tweak = 1.30) 
rpart.plot(tree_1, box.palette="GnOr", main="(b) Interaction frequency for subset with floral rewards", cex.main=1.75,tweak = 1.30)

rpart.plot(tree2, box.palette="GnOr", main="(c) Normalized degree for all with species", cex.main=1.75,tweak = 1.30)
rpart.plot(tree_2, box.palette="GnOr", main="(d) Normalized degree for subset with floral rewards", cex.main=1.75,tweak = 1.30)

rpart.plot(tree3, box.palette="GnOr", main="(e) Specialization for all species", cex.main=1.75,tweak = 1.30)
rpart.plot(tree_3, box.palette="GnOr", main="(f) Specialization for subset with floral rewards", cex.main=1.75,tweak = 1.30)

>>>>

rpart.plot(tree_1, box.palette="GnOr", main="(a) Interaction frequency for all species", cex.main=1.75,tweak = 1.30) 
rpart.plot(tree1, box.palette="GnOr", main="(b) Interaction frequency for subset with floral rewards", cex.main=1.75,tweak = 1.30)

rpart.plot(tree_2, box.palette="GnOr", main="(c) Normalized degree for all species", cex.main=1.75,tweak = 1.30)
rpart.plot(tree2, box.palette="GnOr", main="(d) Normalized degree for subset with floral rewards", cex.main=1.75,tweak = 1.30)

rpart.plot(tree_3, box.palette="GnOr", main="(f) Specialization for all species", cex.main=1.75,tweak = 1.30) 
rpart.plot(tree3, box.palette="GnOr", main="(e) Specialization for subset with floral rewards", cex.main=1.75,tweak = 1.30)
